---
title: "Frequentist Modelling"
output: html_document
date: "2025-04-08"
---

```{r setup, include=FALSE}
#install.packages(c("lme4", "Matrix", "brms", "ggplot2", "glmmTMB"))
#install.packages("lmerTest")
#knitr::opts_chunk$set(echo = TRUE)

library(glmmTMB)
library(tidyverse)
library(lme4)
library(lmerTest)

## cosmetic
theme_set(theme_bw()+
theme(panel.spacing=grid::unit(0,"lines")))
```

# Read Data
```{r}
setwd("~/OneDrive - The University of Melbourne/Bayesian Updating and Complexity/Code/Analysis")

participant_data <- read.csv("participant_data.csv")
```

# Transform Data

To fit a Beta regression, decision quality values must lie strictly between 0 and 1. We transform all decision quality values equal to 0 to 10^{-10}, and those equal to 1 to (1 - 10^{-10})

```{r}
# Specify the column names to transform
cols <- c("DQ_U_o", "DQ_U_s", "DQ_C_o", "DQ_C_s")

# Apply the transformation to each specified column in participant_data
participant_data[cols] <- lapply(participant_data[cols], function(x) {
  ifelse(x == 0, 10^(-1), ifelse(x == 1, 1 - 10^(-1), x))
})

```

To fit beta regression, it is the best practice to have the regressor to be standardized

```{r}
participant_data <- participant_data %>%
  mutate(
    urns_trans    = as.numeric(scale(urns)),
    colours_trans = as.numeric(scale(colours)),
    seqBall_trans = as.numeric(scale(seqBall)),
    DV_seqBall_1_trans = as.numeric(scale(DV_seqBall_1)),
    DV_seqBall_2_trans = as.numeric(scale(DV_seqBall_2)),
    DV_seqBall_3_trans = as.numeric(scale(DV_seqBall_3)),
    ACC_u_trans = as.numeric(scale(ACC_u)),
    ACC_c_trans = as.numeric(scale(ACC_c)),
    CC_u_trans = as.numeric(scale(CC_u)),
    CC_c_trans = as.numeric(scale(CC_c)),
  )
```

# Data Visualisation 

To detect whether random intercept and random slopes are needed

```{r}
# Convert participantID to character in base R
participant_data$participantID <- as.character(participant_data$participantID)

cols <- c("DQ_U_o", "DQ_U_s", "DQ_C_o", "DQ_C_s")
# Multiple regressions by participant
for (i in cols){
  p <- ggplot(participant_data, aes(x = colours, y = !!sym(i), color = participantID)) +
    # One regression line per participant (colored by participantID)
    geom_smooth(
      method = "lm",
      se = FALSE,
      linewidth = 0.3
    ) +
    # Points (also colored by participantID)
    geom_point() +
    labs(
      x = "colours",
      y = i
    ) +
    theme_minimal()
  
  print(p)
}

```


# Data Modelling



```{r}
# Set up the factorized participant ID
participant_data$participantID <- as.factor(as.character(participant_data$participantID))

# R1
model <- glmmTMB(DQ_U_o ~ ACC_u + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R2
model <- glmmTMB(DQ_C_o ~ ACC_c + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
# Warning: NA/NaN function evaluation. This warning occurs when the optimizer visits a region of parameter space that is invalid. It is not a problem as long as the optimizer has left that region of parameter space upon convergence, which is indicated by an absence of the model convergence warnings described above. The following warnings indicate possibly-transient numerical problems with the fit, and can be treated in the same way (i.e. ignored if there are no errors or convergence warnings about the final fitted model).
summary(model)
```

```{r}
# R3
model <- glmmTMB(DQ_U_o ~ urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)

```

```{r}
# R4
model <- glmmTMB(DQ_C_o ~ urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R5
model <- glmmTMB(DQ_U_s ~ CC_u + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R6
model <- glmmTMB(DQ_C_s ~ CC_c + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R7
model <- glmmTMB(DQ_U_o ~ DV_bayesInExp + sex + age + (1 |  instanceName) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R8
model <- glmmTMB(DQ_C_o ~  DV_bayesInExp + sex + age + (1 | instanceName) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R9
model <- glmmTMB(DQ_U_s ~ DV_seqBall_1 + DV_seqBall_3 + (1 | participantID + instanceName) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
print(summary(model))
# logit(u) = log(u/(1-u)) = ata = X*beta + Z*b
# This leads to u = exp(eta) / (1+exp(eta))

# Calculate eta when both DV_seqBall_1 = DV_seqBall_3 = 0. 
# i.e. The average decision quality for two-ball-drawn trials
parameters = model[2]$fit$par
eta_2BD = parameters[1]
u_2BD = exp(eta_2BD) / (1+exp(eta_2BD))
cat(sprintf("The average decision quality for two-ball-drawn trials is %.3f \n", u_2BD))

# Calculate eta when DV_seqBall_1 = 1 
# i.e. The average decision quality for one-ball-drawn trials
eta_1BD = parameters[1] + parameters[2]
u_1BD = exp(eta_1BD) / (1+exp(eta_1BD))
cat(sprintf("The average decision quality for one-ball-drawn trials is %.3f \n", u_1BD))

# Calculate eta when DV_seqBall_3 = 1 
# i.e. The average decision quality for three-ball-drawn trials
eta_3BD = parameters[1] + parameters[3]
u_3BD = exp(eta_3BD) / (1+exp(eta_3BD))
cat(sprintf("The average decision quality for three-ball-drawn trials is %.3f \n", u_3BD))

diff_1_2 = (u_1BD - u_2BD) * 100
diff_1_3 = (u_1BD - u_3BD) * 100
cat(sprintf("Decision quality in one-ball-drawn trials are on average %.2f percentage points higher than two-ball-drawn trials and %.2f percentage point higher than three-ball-drawn trials \n", diff_1_2, diff_1_3))
```

```{r}
# R10
model <- glmmTMB(DQ_U_s ~ DV_seqBall_2 + DV_seqBall_3 + (1 | participantID + instanceName) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)

# Calculate eta when both DV_seqBall_1 = DV_seqBall_3 = 0. 
# i.e. The average decision quality for one-ball-drawn trials
parameters = model[2]$fit$par
eta_1BD = parameters[1]
u_1BD = exp(eta_1BD) / (1+exp(eta_1BD))
cat(sprintf("The average decision quality for one-ball-drawn trials is %.2f \n", u_1BD))

# Calculate eta when DV_seqBall_1 = 1 
# i.e. The average decision quality for two-ball-drawn trials
eta_2BD = parameters[1] + parameters[2]
u_2BD = exp(eta_2BD) / (1+exp(eta_2BD))
cat(sprintf("The average decision quality for two-ball-drawn trials is %.2f \n", u_2BD))

# Calculate eta when DV_seqBall_3 = 1 
# i.e. The average decision quality for three-ball-drawn trials
eta_3BD = parameters[1] + parameters[3]
u_3BD = exp(eta_3BD) / (1+exp(eta_3BD))
cat(sprintf("The average decision quality for three-ball-drawn trials is %.2f \n", u_3BD))
```

```{r}
# R11
model <- lmer(responseTimeUrn ~ CC_u + (1 | participantID + seqBall), data = participant_data)
summary(model)
```

```{r}
# R12
model <- lmer(responseTimeColour ~ CC_c + (1 | participantID + seqBall), data = participant_data)
summary(model)
```
```{r}
# R13
model <- glmmTMB(DQ_U_o ~ ACC_u + responseTimeUrn + ACC_u * responseTimeUrn + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)

# Warning: NA/NaN function evaluation. This warning occurs when the optimizer visits a region of parameter space that is invalid. It is not a problem as long as the optimizer has left that region of parameter space upon convergence, which is indicated by an absence of the model convergence warnings described above. The following warnings indicate possibly-transient numerical problems with the fit, and can be treated in the same way (i.e. ignored if there are no errors or convergence warnings about the final fitted model).
```

```{r}
# R14
model <- glmmTMB(DQ_C_o ~ ACC_c + responseTimeColour + ACC_c * responseTimeColour + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
# Warning: NA/NaN function evaluation. This warning occurs when the optimizer visits a region of parameter space that is invalid. It is not a problem as long as the optimizer has left that region of parameter space upon convergence, which is indicated by an absence of the model convergence warnings described above. The following warnings indicate possibly-transient numerical problems with the fit, and can be treated in the same way (i.e. ignored if there are no errors or convergence warnings about the final fitted model).
```



```{r}
# R15
model <- glmmTMB(DQ_U_o ~ ACC_u + urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```

```{r}
# R16
model <- glmmTMB(DQ_U_s ~ CC_u + urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```
```{r}
# R17
model <- glmmTMB(DQ_C_o ~ ACC_c + urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```


```{r}
# R18
model <- glmmTMB(DQ_C_s ~ CC_c + urns + colours + seqBall + (1 | participantID) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
summary(model)
```


```{r}
# R19
model <- glmmTMB(DQ_C_s ~ DV_seqBall_1 + DV_seqBall_3 + (1 | participantID + instanceName) , data = participant_data, family = glmmTMB::beta_family(link = "logit"))
print(summary(model))
# logit(u) = log(u/(1-u)) = ata = X*beta + Z*b
# This leads to u = exp(eta) / (1+exp(eta))

# Calculate eta when both DV_seqBall_1 = DV_seqBall_3 = 0. 
# i.e. The average decision quality for two-ball-drawn trials
parameters = model[2]$fit$par
eta_2BD = parameters[1]
u_2BD = exp(eta_2BD) / (1+exp(eta_2BD))
cat(sprintf("The average decision quality for two-ball-drawn trials is %.3f \n", u_2BD))

# Calculate eta when DV_seqBall_1 = 1 
# i.e. The average decision quality for one-ball-drawn trials
eta_1BD = parameters[1] + parameters[2]
u_1BD = exp(eta_1BD) / (1+exp(eta_1BD))
cat(sprintf("The average decision quality for one-ball-drawn trials is %.3f \n", u_1BD))

# Calculate eta when DV_seqBall_3 = 1 
# i.e. The average decision quality for three-ball-drawn trials
eta_3BD = parameters[1] + parameters[3]
u_3BD = exp(eta_3BD) / (1+exp(eta_3BD))
cat(sprintf("The average decision quality for three-ball-drawn trials is %.3f \n", u_3BD))

diff_1_2 = (u_1BD - u_2BD) * 100
diff_1_3 = (u_1BD - u_3BD) * 100
cat(sprintf("Decision quality in one-ball-drawn trials are on average %.2f percentage points higher than two-ball-drawn trials and %.2f percentage point higher than three-ball-drawn trials \n", diff_1_2, diff_1_3))
```



