---
title: "Bayesian Regressions"
output: html_document
date: "2025-03-21"
---

```{r setup, include=FALSE}
#install.packages("brms","dplyr")
#install.packages("devtools")
#devtools::install_github("tidyverse/tidyverse")
#devtools::install_github("thomasp85/gganimate")

knitr::opts_chunk$set(echo = TRUE)
library(brms)
library(dplyr)
library(tidyverse)
library(bayesplot)
```

# Read Data

```{r}
setwd("~/OneDrive - The University of Melbourne/Bayesian Updating and Complexity/Code/Analysis")

participant_data <- read.csv("participant_data.csv")


```

# Transform Data


To fit Bayesian regression, it is the best practice to standardize the regressors



```{r}
n <- nrow(participant_data)
participant_data <- participant_data %>%
  mutate(
    urns_trans    = as.numeric(scale(urns)),
    colours_trans = as.numeric(scale(colours)),
    seqBall_trans = as.numeric(scale(seqBall)),
    ACC_u_trans = as.numeric(scale(ACC_u)),
    ACC_c_trans = as.numeric(scale(ACC_c)),
    CC_u_trans = as.numeric(scale(CC_u)),
    CC_c_trans = as.numeric(scale(CC_c)),
  )
```

To fit a Beta regression, decision quality values must lie strictly between 0 and 1. We transform all decision quality values equal to 0 to 10^{-10}, and those equal to 1 to (1 - 10^{-10})


```{r}
# Specify the column names to transform
cols <- c("DQ_U_o", "DQ_U_s", "DQ_C_o", "DQ_C_s")

# Apply the transformation to each specified column in participant_data
participant_data[cols] <- lapply(participant_data[cols], function(x) {
  ifelse(x == 0, 10^(-1), ifelse(x == 1, 1 - 10^(-1), x))
})

```

# H1-B

In the state updating question, decision quality does not decrease as the number of potential signals (number of possible colors) in an instance increase, since more potential signals does not increase computational complexity.


## Visualising H1-B using random intercept simple linear regressions
```{r}
# Simple linear regression (pooled across participants)
ggplot(participant_data, aes(x = colours, y = DQ_U_o_trans)) +
  # Single global regression line in black
  geom_smooth(
    data = participant_data, 
    aes(x = colours, y = DQ_U_o),
    method = "lm", 
    inherit.aes = FALSE, 
    se = FALSE, 
    color = "black", 
    linewidth = 0.9
  ) +
  # Points
  geom_point(aes(x = colours, y = DQ_U_o)) +
  labs(
    x = "colours",
    y = "DQ_U_o"
  ) +
  theme_minimal()


# Convert participantID to character in base R
participant_data$participantID <- as.character(participant_data$participantID)
# Multiple regressions by participant
ggplot(participant_data, aes(x = colours, y = DQ_U_o, color = participantID)) +
  # One regression line per participant (colored by participantID)
  geom_smooth(
    method = "lm",
    se = FALSE,
    linewidth = 0.9
  ) +
  # Points (also colored by participantID)
  geom_point() +
  labs(
    x = "colours",
    y = "DQ_U_o"
  ) +
  theme_minimal()
```
# Bayesian Regressions

## Set Priors

```{r}
# Diffuse Priors
# Define priors for the model:
# - Fixed effects (slopes and intercept): Normal(0, 1000000)
# - Random intercept standard deviation: Half-Cauchy(0, 1)
# - Beta precision parameter (phi): Gamma(2, 0.1)
diffuse_priors <- c(
  set_prior("normal(0, 1000000)", class = "b"),
  set_prior("normal(0, 1000000)", class = "Intercept"),
  set_prior("cauchy(0, 1)", class = "sd", lb = 0),
  set_prior("gamma(2, 0.1)", class = "phi")
)

# Priors for regression have no independent variables - remove the class = b prior
diffuse_priors_nb <- c(
  set_prior("normal(0, 1000000)", class = "Intercept"),
  set_prior("cauchy(0, 1)", class = "sd", lb = 0),
  set_prior("gamma(2, 0.1)", class = "phi")
)

```


```{r}
options(brms.verbose = FALSE)

# Regression 1 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r1_diffuse <- brm(
  formula = DQ_U_o ~ urns_trans + colours_trans + seqBall_trans + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r1_diffuse))
#print(plot(r1_diffuse))

# Regression 2 - Diffuse
r2_diffuse <- brm(
  formula = DQ_U_o ~ urns_trans + seqBall_trans + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r2_diffuse))
#print(plot(r2_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_1 <- bridge_sampler(r1_diffuse)
bridge_2 <- bridge_sampler(r2_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_21 > 3
BF_21 <- bridgesampling::bf(bridge_2, bridge_1)
print(BF_21)

if (BF_21[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H1-B")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H1-B")
}

```

```{r}
#names(participant_data)

# Regression 3 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r3_diffuse <- brm(
  formula = DQ_U_s ~ DV_seqBall_1 + DV_seqBall_3 + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r3_diffuse))
#print(plot(r3_diffuse))

# Regression 4 - Diffuse
r4_diffuse <- brm(
  formula = DQ_U_s ~ DV_seqBall_1 + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r4_diffuse))
#print(plot(r4_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_3 <- bridge_sampler(r3_diffuse)
bridge_4 <- bridge_sampler(r4_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_43 > 3
BF_43 <- bridgesampling::bf(bridge_4, bridge_3)
print(BF_43)

if (BF_43[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H2-C")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H2-C")
}
```

```{r}
# Regression 5 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r5_diffuse <- brm(
  formula = DQ_C_s ~ DV_seqBall_1 + DV_seqBall_3 + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r5_diffuse))
#print(plot(r5_diffuse))


# Regression 6 - Diffuse
r6_diffuse <- brm(
  formula = DQ_C_s ~  (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors_nb,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r6_diffuse))
#print(plot(r6_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_5 <- bridge_sampler(r5_diffuse)
bridge_6 <- bridge_sampler(r6_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_65 > 3
BF_65 <- bridgesampling::bf(bridge_6, bridge_5)
print(BF_65)

if (BF_65[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H4-A")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H4-A")
}
```

```{r}
# Regression 7 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r7_diffuse <- brm(
  formula = DQ_U_o ~ ACC_u + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r7_diffuse))
#print(plot(r7_diffuse))


# Regression 7 Control - Diffuse
r7c_diffuse <- brm(
  formula = DQ_U_o ~  (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors_nb,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r7c_diffuse))
#print(plot(r7c_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_7 <- bridge_sampler(r7_diffuse)
bridge_7c <- bridge_sampler(r7c_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_77c > 3
BF_77c <- bridgesampling::bf(bridge_7, bridge_7c)
print(BF_77c)

if (BF_77c[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H1")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H1")
}
```

```{r}
# Regression 8 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r8_diffuse <- brm(
  formula = DQ_C_o ~ ACC_c + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r8_diffuse))
#print(plot(r8_diffuse))


# Regression 8c Control - Diffuse
r8c_diffuse <- brm(
  formula = DQ_C_o ~  (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors_nb,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r8c_diffuse))
#print(plot(r8c_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_8 <- bridge_sampler(r8_diffuse)
bridge_8c <- bridge_sampler(r8c_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_88c > 3
BF_88c <- bridgesampling::bf(bridge_8, bridge_8c)
print(BF_88c)

if (BF_88c[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H3")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H3")
}
```


```{r}
# Regression 9 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r9_diffuse <- brm(
  formula = DQ_U_s ~ CC_u + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r9_diffuse))
#print(plot(r9_diffuse))


# Regression 9 Control - Diffuse
r9c_diffuse <- brm(
  formula = DQ_U_s ~  (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors_nb,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r9c_diffuse))
#print(plot(r9c_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_9 <- bridge_sampler(r9_diffuse)
bridge_9c <- bridge_sampler(r9c_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_99c > 3
BF_99c <- bridgesampling::bf(bridge_9, bridge_9c)
print(BF_99c)

if (BF_99c[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H2")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H2")
}
```

```{r}
# Regression 10 - Diffuse
# Fit the hierarchical Bayesian beta regression model using the transformed response
r10_diffuse <- brm(
  formula = DQ_C_s ~ CC_c + (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)
print(summary(r10_diffuse))
#print(plot(r10_diffuse))


# Regression 10 Control - Diffuse
r10c_diffuse <- brm(
  formula = DQ_C_s ~  (1 | participantID),
  data = participant_data,
  family = Beta(link = "logit"),
  prior = diffuse_priors_nb,
  chains = 4,
  iter = 2000,
  warmup = 1000,
  seed = 123,
  save_pars = save_pars(all = TRUE),
  control = list(adapt_delta = 0.95),
  silent = TRUE,
  refresh = 0
)

print(summary(r10c_diffuse))
#print(plot(r10c_diffuse))

# Compute marginal likelihoods via bridgesampling for each model
bridge_10 <- bridge_sampler(r10_diffuse)
bridge_10c <- bridge_sampler(r10c_diffuse)

# Calculate the Bayes factor (BF) comparing Model A to Model B.
# BF_1010c > 3
BF_1010c <- bridgesampling::bf(bridge_10, bridge_10c)
print(BF_1010c)

if (BF_1010c[1] > 3) {
  print("Random Intercept Model(Diffuse Prior) Support H4")
} else {
  print("Random Intercept Model(Diffuse Prior) Does not Support H4")
}
```



